A Formalisation of Sturm Chains in \isabellehol

### 2013-09-09 description/description.tex
Updated description

Based on this, a number of generalisations can be used to count roots of 
polynomials with multiple roots as well, and furthermore, the total number of 
real roots can be determined by using $\lim_{x\to\pm\infty} \sigma(x)$, which 
can be determined by looking at the leading coefficient of the polynomials in 
the chain.

@@

\section{Work outline}
We estimate that the work to be done is the following:
\begin{itemize}
\item Define, with enough generality to allow for later generalisations and optimisations, what 
      properties a general Sturm chain must fulfil
\item Prove that a chain fulfilling these requirements can indeed by used to count roots
\item Prove that the various canonical and non-canonical sturm chains fulfil these requirements
\item Prove that one can determine the signs of polynomials for sufficiently large arguments by 
      looking at the leading coefficients (this may require extension of the Polynomial library,
      since no lemmas about limits of polynomials exist so far)
\item Use these definitions and proofs to implement a decision procedure as described above and 
      integrate it with Isabelle
\end{itemize}

>>>>

Based on this, a number of generalisations can be used to count roots of 
polynomials with multiple roots as well, and furthermore, the total number of 
real roots can be determined by using $\lim_{x\to\pm\infty} \sigma(x)$, which 
can be determined by looking at the leading coefficients of the polynomials in 
the chain.

@@

\section{Work outline}
We estimate that the work to be done is the following:
\begin{itemize}
\item Define, with enough generality to allow for later generalisations and optimisations, what 
      properties a general Sturm chain must fulfil
\item Prove that a chain fulfilling these requirements can indeed be used to count roots
\item Prove that the various canonical and non-canonical sturm chains fulfil these requirements
\item Prove that one can determine the signs of polynomials for sufficiently large arguments by 
      looking at the leading coefficients (this may require extension of the Polynomial library,
      since no lemmas about limits of polynomials exist so far)
\item Use these definitions and proofs to implement a decision procedure as described above and 
      integrate it with Isabelle
\end{itemize}
